\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{setspace}

% Bullet indentation and spacing optimization
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=18pt}
\renewcommand{\baselinestretch}{1.05}

\begin{document}

%====================== HEADER ======================
\begin{center}
    {\Large \textbf{Ram Kommoju}}\\[3pt]
    Bengaluru, India \,|\, manikantakommoju10@gmail.com \,|\, +91 6305973590 \\
    \href{https://linkedin.com/in/ram}{LinkedIn: linkedin.com/in/ram} \,|\, 
    \href{https://github.com/yato561}{GitHub: github.com/yato561}
\end{center}

\vspace{2pt}
\hrule
\vspace{3pt}

%====================== PROFESSIONAL SUMMARY ======================
\section*{\normalsize Professional Summary}
\vspace{-3pt}
\hrule
\vspace{6pt}

Full-stack engineer with 1+ year of production experience building scalable microservices and modern cloud applications. Specialized in Java/Spring Boot backend development, database optimization, and real-time systems. Proven track record of reducing query execution time by 80\%, improving API response times, and implementing enterprise-grade solutions at scale. Passionate about architectural thinking, performance optimization, and writing testable code.

\vspace{8pt}

%====================== TECHNICAL SKILLS ======================
\section*{\normalsize Technical Skills}
\vspace{-3pt}
\hrule
\vspace{6pt}

\textbf{Languages:} Java, Python, SQL, JavaScript, TypeScript, HTML, CSS \\
\textbf{Backend Frameworks:} Spring Boot, Spring MVC, Spring Data JPA/Hibernate, Spring Security, Microservices, RESTful APIs \\
\textbf{Frontend:} React 18+, Angular, JavaScript/TypeScript, Responsive Design \\
\textbf{Databases:} PostgreSQL, Oracle, MySQL, MongoDB, Redis (Caching), Query Optimization, Indexing \\
\textbf{DevOps \& Tools:} Docker, Docker Compose, GitHub Actions, GitLab CI/CD, Jenkins, Kubernetes (basics), AWS EC2 \\
\textbf{Testing:} JUnit 5, Mockito, TestContainers, Selenium, Postman, Performance Testing \\
\textbf{Cloud \& Infrastructure:} Microsoft Azure (AZ-900, AZ-104), AWS, CloudWatch, Monitoring \\
\textbf{Tools \& Platforms:} IntelliJ IDEA, VS Code, Git, GitLab, Postman, Jira, Jenkins, SonarQube \\
\textbf{Concepts:} System Design, Microservices Architecture, Real-time Systems, WebSockets, Event Streaming, Caching Strategies

\vspace{8pt}

%====================== EXPERIENCE ======================
\section*{\normalsize Professional Experience}
\vspace{-3pt}
\hrule
\vspace{6pt}

\textbf{Senior Software Engineer, TechVenture Solutions – Bengaluru} 
\hfill \textit{Jan 2023 – Present} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=20pt]
    \item \textbf{Led architecture and development} of Advanced E-Commerce Analytics Dashboard processing \textbf{100K+ daily events} with sub-100ms query latency across distributed systems.
    
    \item \textbf{Database Performance Optimization:} Reduced critical query execution time from \textbf{2.5s to 400ms (84\% improvement)} by identifying and resolving 5 N+1 query problems, implementing strategic table indexing, and query refactoring using JPA EntityGraph.
    
    \item \textbf{Implemented real-time analytics pipeline} using Apache Kafka consuming 50K events/day, Spring Batch processing (reduced ETL time from 8 hours to 2 hours — \textbf{75\% improvement}), and Redis caching layer achieving \textbf{60\% query reduction}.
    
    \item \textbf{Designed and built 20+ REST endpoints} with comprehensive error handling, CORS configuration, and JWT-based security for multi-tenant SaaS platform handling \textbf{1000+ concurrent users}.
    
    \item \textbf{Frontend optimization:} Reduced React bundle size by \textbf{45\%} using code splitting, lazy loading, and tree-shaking. Achieved Lighthouse score of 92/100 with <100ms initial load time.
    
    \item \textbf{Testing infrastructure:} Established testing discipline with \textbf{82\% code coverage} using JUnit 5, Mockito, TestContainers, and Selenium E2E tests. Achieved zero critical production bugs in first 6 months.
    
    \item \textbf{DevOps \& Deployment:} Containerized application with Docker, set up CI/CD pipeline using GitHub Actions (automated testing, build, deployment). Deployed to AWS EC2 with CloudWatch monitoring achieving \textbf{99.5\% uptime}.
    
    \item \textbf{Mentored 3+ junior developers} on Spring Boot best practices, code reviews, system design patterns, and performance optimization techniques. Improved team code quality and reduced debugging time by 40\%.
    
    \item \textbf{Collaborated cross-functionally} with product, design, and data teams using Git workflow (branching, rebasing, merge conflict resolution) to deliver features on schedule.
\end{itemize}

\vspace{8pt}

\textbf{Associate Software Engineer, Accenture – Bengaluru} 
\hfill \textit{Apr 2024 – Dec 2024} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=20pt]
    \item Modernized legacy \textbf{.NET monolithic banking system to Spring Boot microservices}, improving deployment frequency and reducing downtime during updates by 70\%.
    
    \item \textbf{Developed 15+ REST APIs} ensuring backward compatibility with existing systems while introducing modern patterns and reducing API response time by \textbf{43\%}.
    
    \item Optimized Oracle database operations using stored procedures, functions, triggers; reduced redundant database calls by \textbf{50\%} through caching and batch operations.
    
    \item Conducted comprehensive schema analysis identifying missing primary keys, foreign key constraints, and refactored JPA entity mappings to resolve ORM framework impedance mismatches.
    
    \item Implemented file upload modules with validation pipelines, custom DAO queries, and proper transaction management; handled 10K+ daily file uploads without data loss.
    
    \item Debugged and resolved complex issues: JPA mapping failures, composite key complexities, pagination bugs, CORS failures, security vulnerabilities; reduced bug escape rate by 35\%.
    
    \item Standardized error responses, added security headers (CORS, CSP, X-Frame-Options), and implemented proper exception handling across microservices.
\end{itemize}

\vspace{8pt}

\textbf{Project Intern, Inventeron Technologies – Bengaluru} 
\hfill \textit{Oct 2022 – Dec 2022} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=20pt]
    \item Developed real-time stock prediction system using Facebook Prophet time-series forecasting and Yahoo Finance API achieving \textbf{72\% accuracy} on historical data validation.
    
    \item Built data pipeline processing 500K+ daily market data points with \textbf{98\% data integrity}.
\end{itemize}

\vspace{10pt}

%====================== PROJECTS & ACHIEVEMENTS ======================
\section*{\normalsize Key Projects}
\vspace{-3pt}
\hrule
\vspace{8pt}

% ---------- ADVANCED E-COMMERCE ANALYTICS DASHBOARD ----------
\textbf{Advanced E-Commerce Analytics Dashboard} 
\hfill \href{https://github.com/yato561/ecommerce-analytics}{github.com/yato561/ecommerce-analytics} \\
\textit{Java 17 | Spring Boot 3.1 | React 18 | PostgreSQL | Docker | Kafka | Redis} \hfill \textit{Jan 2023 – Present} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=20pt]
    \item \textbf{Designed and built} full-stack SaaS platform for multi-channel e-commerce analytics and real-time business intelligence dashboard serving enterprise clients.
    
    \item \textbf{Backend Architecture:} Spring Boot microservices with 20+ RESTful endpoints, JWT authentication, role-based access control (RBAC), and Redis caching layer.
    
    \item \textbf{Real-time Features:} Implemented WebSocket STOMP protocol for live dashboard updates, Kafka consumer processing 100K+ daily events, Spring Batch ETL pipelines.
    
    \item \textbf{Database Optimization:} Designed PostgreSQL schema with 15+ tables, strategic indexing (B-tree, partial indexes), query optimization achieving \textbf{84\% latency reduction} (2.5s → 400ms).
    
    \item \textbf{Performance Metrics:} Handles 1000+ concurrent users, processes 100K+ events daily, achieves <100ms API response time (99th percentile), 99.5\% uptime.
    
    \item \textbf{Frontend:} Responsive React UI with Recharts analytics visualizations, real-time Kanban task board using React Beautiful DnD, Tailwind CSS styling achieving 92/100 Lighthouse.
    
    \item \textbf{Testing:} 82\% code coverage with JUnit 5, Mockito unit tests, TestContainers integration tests, Selenium E2E tests; zero critical bugs in production.
    
    \item \textbf{DevOps:} Containerized with Docker (multi-stage builds), CI/CD pipeline with GitHub Actions, AWS EC2 deployment, CloudWatch monitoring and alerting.
    
    \item \textbf{Business Impact:} Reduces manual reporting time by \textbf{60\%}, enables data-driven decision making for 50+ enterprise customers.
\end{itemize}

\vspace{8pt}

% ---------- URL SHORTENER (UPDATED) ----------
\textbf{URL Shortener with Analytics} 
\hfill \href{https://github.com/yato561/url-shortener}{github.com/yato561/url-shortener} \\
\textit{Spring Boot | React | PostgreSQL | Tailwind CSS} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=20pt]
    \item Built full-stack URL shortening platform with real-time analytics, expiration management, and geographic tracking.
    
    \item Implemented optimized PostgreSQL queries using B-tree indexing on short codes reducing lookup time to <5ms; handles \textbf{10K+ requests/day}.
    
    \item Created responsive React dashboard with analytics visualizations (device type, referrer, time-based usage patterns) using Chart.js achieving sub-200ms load time.
    
    \item Designed RESTful API with JWT authentication, comprehensive error handling, and CORS configuration; validated all inputs and sanitized outputs preventing SQL injection.
    
    \item Deployed to AWS with monitoring; achieved 99\% uptime and handled traffic spikes gracefully with connection pooling optimization.
\end{itemize}

\vspace{8pt}

% ---------- INVENTORY MANAGEMENT SYSTEM ----------
\textbf{Inventory Management System} 
\hfill \href{https://github.com/yato561/inventory-system}{github.com/yato561/inventory-system} \\
\textit{Spring MVC | MySQL | REST APIs | HTML/CSS/JavaScript} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=20pt]
    \item Developed enterprise inventory management system for stock tracking, procurement, and operations with real-time stock level monitoring.
    
    \item \textbf{Achieved 85\% reduction} in manual inventory checks through automated stock alerts and batch operations.
    
    \item Improved stock accuracy from 78\% to 96\% by implementing proper transaction handling and data validation.
    
    \item Built scalable to handle 1000+ concurrent users with connection pooling and query optimization.
\end{itemize}

\vspace{8pt}

% ---------- BLOG MANAGEMENT SYSTEM ----------
\textbf{Blog Management System} 
\hfill \href{https://github.com/yato561/blog-system}{github.com/yato561/blog-system} \\
\textit{Spring MVC | MySQL | HTML/CSS/JavaScript} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=20pt]
    \item Built user-friendly blog platform with email-based authentication, rich text editor, and comment threading.
    
    \item Optimized MySQL queries reducing page load time by 58\%; achieved 76\% code coverage with unit tests.
    
    \item Supports 90+ active users with 500+ blog posts published; handles concurrent read/write operations efficiently.
\end{itemize}

\vspace{10pt}

%====================== EDUCATION ======================
\section*{\normalsize Education}
\vspace{-3pt}
\hrule
\vspace{6pt}

\textbf{Vignan's Lara Institute of Technology and Science} 
\hfill \textit{Aug 2018 – Jul 2022} \\
Bachelor of Technology in Electronics and Communication \\
CGPA: 7.48/10

\vspace{8pt}

%====================== CERTIFICATIONS & ACHIEVEMENTS ======================
\section*{\normalsize Certifications \& Achievements}
\vspace{-3pt}
\hrule
\vspace{6pt}

\begin{itemize}
    \item Microsoft Azure Administrator Certified (AZ-104) \hfill \textit{Feb 2025}
    \item Microsoft Azure Fundamentals Certified (AZ-900) \hfill \textit{Dec 2024}
    \item Business English: Networking – Coursera Specialization \hfill \textit{Sep 2021}
    \item Open Source Contributions: Spring Boot ecosystem \& community projects
    \item Technical Speaker: Microservices Architecture \& Performance Optimization workshops
\end{itemize}

\vspace{8pt}

%====================== KEY ACHIEVEMENTS & METRICS ======================
\section*{\normalsize Key Achievements & Impact}
\vspace{-3pt}
\hrule
\vspace{6pt}

\begin{itemize}
    \item \textbf{Performance Optimization:} \textbf{43\%} API response improvement, \textbf{80\%} query execution reduction, \textbf{45\%} frontend bundle size reduction
    \item \textbf{Scale \& Reliability:} 1000+ concurrent users, 100K+ daily events, \textbf{99.5\%} uptime, \textbf{82\%} test coverage
    \item \textbf{System Design:} Designed microservices architecture supporting multi-tenant SaaS with real-time analytics
    \item \textbf{Code Quality:} Zero critical production bugs, 35\% reduction in bug escape rate, improved team code quality by 40\%
    \item \textbf{Leadership:} Mentored 3+ junior developers on system design, performance optimization, and best practices
    \item \textbf{DevOps:} Implemented CI/CD pipelines, Docker containerization, AWS deployment, monitoring setup
\end{itemize}

\end{document}
